---
title: "ModelFramework"
author: "Brandon Chacso"
date: "12/17/2021"
<<<<<<< HEAD
output: pdf_document
=======
output: html_document
>>>>>>> 7e12c317f9741d96d2287bb71a9ab1b418107d9f
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
<<<<<<< HEAD
juv <- read.csv("../JuvData.csv")
=======
juv <- read.csv("JuvData.csv")
>>>>>>> 7e12c317f9741d96d2287bb71a9ab1b418107d9f
library(glmmTMB)
library(ggplot2)
```

## Model

Notes to myself

* Find the best predictors of juveniles densities
* Should we care predictability
** We want to predict occurrence and abundance to prioritize management action
*** Changing covariates in the future.

Mixed effects models
* Covariance model
* The regression coefficients would be a map
* Time varying coefficients

* Packages

bmrs, glmmTMB

zero-inflated negative binomial


* 
##Data 

Sample sizes

```{r, echo=FALSE}
#
knitr::kable(t(table(juv$Stratum, juv$JuvYr)), 
             caption = "Sample sizes by stratum and year.")

```

<<<<<<< HEAD

#Methods

To examine 

=======
>>>>>>> 7e12c317f9741d96d2287bb71a9ab1b418107d9f
##glmmTMB

```{r}
trainJuv <- juv[juv$JuvYr<max(juv$JuvYr),]
predJuv <- juv[juv$JuvYr==max(juv$JuvYr),]

#Stream yr independent
juv_ziNB_yr_Stratum <- glmmTMB(Juv.km~StrmSlope + MaxGradD + (1|Stratum) +(1|JuvYr),
                    data=trainJuv,
                    ziformula=~1,
                    family=nbinom1)

<<<<<<< HEAD
trainJuv$pos <- numFactor(scale(trainJuv$UTM_E), scale(trainJuv$UTM_E))
#Stream year and stratum, independent AR1 processes for each stream
#This ar1 notation seems very backwards to me
juv <- glmmTMB(Juv.km ~ 
                                     exp(pos+0|ESU) #+
                                    # MWMT_Index +
#                                     SolMean +
#                                     STRM_ORDER +
#                                     StrmSlope + 
#                                     MaxGradD + 
#                                     WidthM +
#                                     OUT_DIST + 
#                                     StrmPow +
#                                     MAnnSed +
                                     # Barriers
                                     ,
                    data=trainJuv,
                    ziformula=~1,
                    verbose = TRUE,
                    family=nbinom1)

 re <- ranef(juv_ziNB_ar1_yr_stratum)

                          # year = c("JuvYr","s(JuvYr)",""),
                          # space = c("s(UTM_E, UTM_N)","s(UTM_E, UTM_N,JuvYr)",""),
                          # req = "s(MWMT_Index,k=4) + s(W3Dppt,k=4) + s(SprPpt,k=4) + s(IP_COHO,k=4)",
                          # sol = c("s(SolMean,k=4)",""),
                          # strm = c("STRM_ORDER"),
                          # rnk = c("s(CLASS_Rank,k=3)",""),
                          # cov1 = c("s(StrmSlope,k=4)"),
                          # cov2 = c("s(MaxGradD,k=4)"),
                          # cov3 = c("s(WidthM,k=4)",""),
                          # cov4 = c("s(OUT_DIST,k=4)",""),
                          # cov5 = c("s(StrmPow,k=4)",""),
                          # cov6 = c("s(MAnnSed,k=4)",""),
                          # cov7 = c("s(Barriers,k=4)",""),

=======
#Stream year and stratum, independent AR1 processes for each stream
#This ar1 notation seems very backwards to me
juv_ziNB_ar1_yr_stratum <- glmmTMB(Juv.km~StrmSlope + MaxGradD + ar1(Stratum+0|JuvYr),
                    data=trainJuv,
                    ziformula=~1,
                    family=nbinom1)

>>>>>>> 7e12c317f9741d96d2287bb71a9ab1b418107d9f
#Stream year and stratum, uncorrelated processes for each stream
#Computationally too expensive, >1 min = too long
#Distance between stratum would reduced dimensionality and speed estimation
#could use ou covariance structure
# juv_ziNB_us_yr_stratum <- glmmTMB(Juv.km~StrmSlope + MaxGradD + us(as.factor(JuvYr)+0|Stratum),
#                     data=trainJuv,
#                     # dispformula=~0,
#                     ziformula=~(1|Stratum),
#                     family=nbinom1)


pred_mod1 <- predict(juv_ziNB_yr_Stratum, 
                     newdata= predJuv)

pred_mod2 <- predict(juv_ziNB_ar1_yr_stratum, 
                     newdata= predJuv,
                     allow.new.levels = TRUE)

MAE <- data.frame(mod1=sum(abs(exp(pred_mod1)-predJuv$Juv.km)),
                  mod2=sum(abs(exp(pred_mod2)-predJuv$Juv.km)))

print(MAE)

```

```{r}
re_mod1 <- ranef(juv_ziNB_yr_Stratum)
re_mod2 <- ranef(juv_ziNB_ar1_yr_stratum)
matplot(re_mod1$cond$JuvYr,
        type="l",
        lwd=3)
matplot(re_mod2$cond$JuvYr,
        type="l")
```
